R Notebook

### 2021-06-21 Exemples and Implementations.Rmd
example and implementation aggiornamenti in arrivo

```{r include=FALSE}
# Data and prior hyperparameters 
# ------------------------------
m0      = 0.0
C0      = 0.1
sC0     = sqrt(C0)
ealpha  = alpha
valpha  = 0.01
ebeta    = beta
vbeta    = 0.01
nu      = 3
lambda  = tau2

# Liu and West filter
# -------------------
set.seed(8642)
N      = 10
```

@@

  mpar        = apply(pars,2,mean)
  vpar        = var(pars)
  ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
  mus         = pars[,1]+pars[,2]*xs 
  weight      = w*dnorm(y[1],0,exp(mus/2))
  k           = sample(1:N,size=N,replace=T,prob=weight)
  ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
  xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
  w           = dnorm(y[1],0,exp(xt/2))/dnorm(y[1],0,exp(mus[k]/2))
  w           = w/sum(w)
  ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
N=1000
svpf<-SVPFfun(y,N,m0,C0,alpha,beta,tau)
svapf<-SVAPFfun(y,N,m0,C0,alpha,beta,tau)
svlw<-SVLWfun(y,N=1000,m0,C0,ealpha=0.12,valpha=0.4,ebeta=1,vbeta=0.3,nu=0.11,lambda=0.1)
```

```{r}
Filtplot(dfsv,svlw,"")
```

>>>>

```{r include=FALSE}
# Data and prior hyperparameters 
# ------------------------------
m0      = 0.0
C0      = 0.1
sC0     = sqrt(C0)
ealpha  = alpha
valpha  = 0.01
ebeta    = beta
vbeta    = 0.01
nu      = 3
lambda  = tau2
```

@@

  #mpar        = apply(pars,2,mean) #alternatively use this 
  mpar<-c()
  for(i in 1:3){
  mpar[i]    = weighted.mean(pars[,i],w)
  }

  vpar        = var(pars)
  ms          = a*pars+(1-a)*matrix(mpar,N,3,byrow=T)
  mus         = pars[,1]+pars[,2]*xs 
  weight      = w*dnorm(y[1],0,exp(mus/2))
  k           = sample(1:N,size=N,replace=T,prob=weight)
  ms1         = ms[k,] + matrix(rnorm(3*N),N,3)%*%chol(h2*vpar)
  xt          = rnorm(N,ms1[,1]+ms1[,2]*xs[k],exp(ms1[,3]/2))
  w           = dnorm(data[t],0,exp(xt/2))/dnorm(data[t],0,exp(mus[k]/2))
  w           = w/sum(w)
  ESS         = 1/sum(w^2)

@@

```{r include=FALSE}
set.seed(12345)
N=5000
svpf<-SVPFfun(y,N,m0,C0,alpha,beta,tau)
svapf<-SVAPFfun(y,N,m0,C0,alpha,beta,tau)
set.seed(1235)
svlw<-SVLWfun(y,N=1000,m0,C0,ealpha=0.12,valpha=0.4,ebeta=1,vbeta=0.3,nu=0.11,lambda=0.1)
```

```{r echo=FALSE, fig.align='center', fig.cap="Kalman Filtered States with credible interval (in red)", fig.height=8, fig.pos='ht', fig.width=8, message=FALSE, warning=FALSE, results=F}
plot1<-Filtplot(dfsv,svpf,"Particle Filter")
plot2<-Filtplot(dfsv,svapf,"Auxiliary Particle Filter")
plot3<-Filtplot(dfsv,svlw,"Liu e West Filter")

ggarrange(plot1,plot2,plot3)
```
